\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black}

\name{Egor Kurbatov} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{St. Petersburg, Russia} 
\address{\href{mailto:luizenbar@gmail.com}{luizenbar@gmail.com} \\ \href{https://www.linkedin.com/in/egor-kurbatov/}{linkedin.com/in/egor-kurbatov} \\
\href{https://github.com/Darui99}{github.com/Darui99} \\
\href{https://t.me/Darui99}{t.me/Darui99}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Computer Science}, ITMO University \hfill {Sep. 2018 - Aug. 2022}

{\bf Moscow Workshops Juniors} \hfill {Feb. 2017}\\
Competitive programming bootcamp

{\bf Summer Informatics School} \hfill {Summer 2016, Summer 2017}\\
Algorithms and Data Structures

{\bf IT Samsung school} \hfill {Sep. 2015 - May 2016}\\
Android software development
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Software Engineer Intern} \hfill Jul. 2021 - Aug. 2021\\
JetBrains \hfill \textit{St. Petersburg, Russia}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Backend developer in Qodana. Kotlin/Java.
 \end{itemize}
 
\textbf{Software Engineer Intern} \hfill Jul. 2019 - Sep. 2019\\
Yandex \hfill \textit{St. Petersburg, Russia}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Backend developer in team of facts and snippets. C++/Python.
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item 
\textbf{Fast hash-based additive accumulators} \hfill \href{https://github.com/Darui99/AdditiveAccumulator}{source link}\\
Cryptographic accumulators. Based on \href{https://github.com/bigspider/accumulator/blob/master/docs/paper-draft.pdf}{this} article. \\ Developed using C++.
 
\item 
\textbf{Markdown contents generator} \hfill \href{https://github.com/Darui99/markdown-contents-generator}{source link}\\
Takes markdown file and generates its table of contents. \\ Developed using Java.

\item 
\textbf{Tournament bot} \hfill \href{https://github.com/Darui99/telegram-game-bot}{source link}\\
Mini Telegram-bot for playing interactive emojis with friends. \\ Developed using Python and Telegram Bot API.
 
\end{rSection} 

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS SECTION	
%----------------------------------------------------------------------------------------

\begin{rSection}{ACHIEVEMENTS} 

{\bf Google Hash Code } \hfill {2022}\\
$164^{th}$ place out of 9000+.

{\bf Northern Eurasia Finals (ICPC semifinal)} \hfill {2019/20}\\
$60^{th}$ place. Third-degree diploma.

{\bf Moscow Open Olympiad in informatics} \hfill {2017/18}\\
$66^{th}$ place out of 2000+. Third-degree diploma.

{\bf Individual Olympiad in informatics} \hfill {2017/18}\\
$19^{th}$ place out of 1000+. First-degree diploma.


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l @{\hspace{6ex}} l}

{\bf Languages:} & Java & {\bf familiar:} C++, Kotlin, Python, Haskell, Go, Matlab \\
{\bf Technologies:} & PostgreSQL, Bash, Git, JUnit & {\bf familiar:} Spring, Vue.js \\
{\bf Knowledge:} & Algorithms, Data Structures & {\bf familiar:} Concurrent Computing, Distributed Systems

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
